D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-23 ootavacuous.tex
Finish changes to causality test case 18
In an earlier patch, I forgot to complete the changes to the comments on
causality test case 18.  Here is the missing material.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

This is the same as causality test case~17, even to the alternate OOTA
cycle reported by the \co{herd7} tool, except that line~9 tests
\co{r3} for equality to zero rather than non-equality to 42.

Perhaps surprisingly, this makes a difference.

@@

This is the same as causality test case~19, even to the OOTA cycle
reported by the \co{herd7} tool, except that line~19 tests
\co{r3} for equality to zero rather than non-equality to 42.
The same analysis applies.

>>>>

This is the same as causality test case~17, even to the alternate OOTA
cycle reported by \co{herd7}, except that line~9 tests
\co{r3} for equality to zero rather than non-equality to 42.
Perhaps surprisingly, this makes a difference.

A compiler that treats atomic objects as volatile or uses
single-thread analysis cannot assume that \co{x} will necessarily be
equal to 42 following lines~9 and~10; it might have some other value
such as 1.
Therefore the compiler cannot conclude that \co{r1} will always be 42
and must leave the semantic dependency between lines~11 and~12 intact.
Of course, the resulting OOTA cycle will not be realized, because of
hardware dependency ordering.

@@

This is the same as causality test case~19, even to the OOTA cycle
reported by \co{herd7}, except that line~19 tests
\co{r3} for equality to zero rather than non-equality to 42.
The same analysis applies.
